### 2024-03-25 doc/sections/mav-semantics.tex
[ tex ] more semantics

\begin{definition}
  An \emph{MAV Algebra} is a structure
  $(A, \leq, \otimes, \rhd, I, \lnot)$ with the following properties:
  \begin{enumerate}
  \item $(A, \leq, \otimes, I, \lnot)$ is $*$-autonomous and satisfies \emph{mix}.
  \item $(A, \leq, \rhd, I)$ is a pomonoid.
  \item $(\otimes, I)$ and $(\rhd, I)$ are in a duoidal relationship.
  \item $(A, \leq)$ has binary meets, which we write as $x \with y$.
  \end{enumerate}
\end{definition}

@@

\begin{proposition}
  There is a monotone function
  $\alpha : \LowerSet{A} \to \ClosedLowerSet{A}$ with the following
  properties. It is a Galois reflection. FIXME
\end{proposition}

@@

@@

  Sketch why this works: we can multiply together the contexts.
\end{proof}

@@

\begin{proof}
  In this case, the Day pomonoid is already closed, by use of the duoidal property.

  \bob{Explain the Agda here}
\end{proof}

@@

\begin{remark}
  We have used the same decoration $\ClosedDay{\bullet}$ and
  $\ClosedDay{\rhd}$ for two separate constructions of pomonoids on
  $+$-closed lower sets. We will be careful to distinguish which we
  mean: a symmetric operator like $\bullet$ 
\end{remark}

@@

The Chu construction allows us to state
directly that any operator we define on $\Chu(A, k)$ is self dual by
defining as the same

\begin{proposition}
  \bob{self dual operators from pomonoids with $k \rhd k \leq k$ and $j \leq k$.}
\end{proposition}

\begin{proposition}
  \bob{duoidality is preserved.}
\end{proposition}

\subsubsection{Complete Construction}

We can now state the second main theorem of this section:

@@

\begin{proof}
  Combining all the propositions above.
\end{proof}

>>>>

\begin{definition}
  An \emph{MAV Algebra} is a structure
  $(A, \leq, \otimes, ;, I, \lnot)$ with the following properties:
  \begin{enumerate}
  \item $(A, \leq, \otimes, I, \lnot)$ is $*$-autonomous and satisfies \emph{mix}.
  \item $(A, \leq, ;, I)$ is a pomonoid.
  \item $(\otimes, I)$ and $(;, I)$ are in a duoidal relationship.
  \item $(A, \leq)$ has binary meets, which we write as $x \with y$.
  \end{enumerate}
\end{definition}

@@

\begin{proposition}
  There is a monotone function
  $\alpha : \LowerSet{A} \to \ClosedLowerSet{A}$ with the following
  properties. It is a Galois reflection. FIXME

  \begin{displaymath}
    \alpha(F) = \{ x \mid c \in \mathrm{ctxt}(F), x \leq \mathit{sum}(c) \}
  \end{displaymath}
\end{proposition}

@@

\begin{remark}
  By this proposition, $U \circ \alpha$ is a closure operator on
  $\LowerSet{A}$ \cite{davey-priestley}, and the closed elements are
  those of $\ClosedLowerSet{A}$. The next proposition is standard for
  showing that meets and joins exist on the closed elements for some
  closure operator.
\end{remark}

@@

  \bob{Sketch why this works: we can multiply together the contexts.}
\end{proof}

@@

@@

\begin{remark}
  We have used the same decoration $\ClosedDay{\bullet}$ and
  $\ClosedDay{\rhd}$ for two separate constructions of pomonoids on
  $+$-closed lower sets. We will be careful to distinguish which we
  mean: a symmetric operator like $\bullet$ will distribute over $+$
  and so $\ClosedDay{\bullet}$ will be constructed by Proposition
  \ref{prop:closed-monoid-distrib}; and a non-symmetric operator like
  $\rhd$ will be entropic with respect to $+$ and so
  $\ClosedDay{\rhd}$ will be constructed by Proposition
  \ref{prop:closed-monoid-duoidal}.
\end{remark}

\begin{remark}
  If we have two $(A, \leq)$ pomonoids with the same unit, then the
  two constructions will yield the same closed lower set.
  \bob{elaborate a bit...}
\end{remark}

@@

\begin{proposition}\label{prop:chu-self-dual}
  Let $(\rhd, j)$ be a pomonoid on $(A, \leq)$ such that
  $k \rhd k \leq k$ and $j \leq k$, then
  $x ; y = (x^+ \rhd y^+, x^- \rhd y^-)$ and $J = (j, j)$ form a
  self-dual pomonoid on $\Chu(A, k)$.
\end{proposition}

\begin{proof}
  \bob{show that that two extra bits are needed.}
\end{proof}

\begin{remark}
  When $k = j$, the two conditions in the proposition are
  automatically satisfied. Moreover, if $k = i = j$, then not only
  does the $*$-autonomous structure satisfy \emph{mix}, but we also
  have $I =J$.
\end{remark}

\begin{proposition}
  If $(\bullet, i)$ and $(\rhd, j)$ are in a duoidal relationship on
  $(A, \leq)$, and $(\rhd, j)$ satisfies the conditions of Proposition
  \ref{prop:chu-self-dual}, then $(\otimes, I)$ and $(;, J)$ are in a
  duoidal relationship on $\Chu(A, k)$.
\end{proposition}

\begin{proof}
  \bob{Explain the Agda}
\end{proof}

\subsection{Construction of MAV-algebras}

@@

\begin{proof}
  Combining all the propositions above, in the special case when some
  of the units collapse.
\end{proof}
